---
title: "hek_analysis"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{hek_analysis}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(RGlycopacity)
```

# loading bulk cancer cell line encyclopedia data 

```{r load_bulk}

ccle_raw_counts.dgeObj <- readRDS(system.file("extdata", "ccle_raw_counts.Rds", package = "RGlycopacity", mustWork = T))

```

```{r}

ccle_log_counts.mat <- edgeR::cpm.DGEList(ccle_raw_counts.dgeObj)+1

```

# computing relative difference for each clusters pseudobulks

```{r}

rel_diff.mat <- normaliseOnSEGs(ccle_log_counts.mat)

```

# computing ranges on relative difference 

```{r}

rel_diff_ranges.mat <- getNormalisedRanges(rel_diff.mat)

```

# computing clrs on relative difference

```{r}

clrs.mat <- transformToCLR(rel_diff.mat)

```

# computing intersect of bulk on bulk

```{r}

bulk_on_bulk_intersect.mat <- calculateNormalisedIntersects(rel_diff.mat, dynamic_ranges.char = 'bulk_ranges')

```

# computing intersect of bulk on single cell

```{r}

bulk_on_sc_intersect.mat <- calculateNormalisedIntersects(rel_diff.mat, dynamic_ranges.char = 'tabula_sapiens_ranges')

```

# loading 2700 pbmc cells from chromium 10x V2

```{r load_sc}

pbmck3k.seurat <- readRDS(system.file("extdata", "pbmc3k.Rds", package = "RGlycopacity", mustWork = T))

```

# computing cluster specific values from raw single cell counts

## trimmed mean pseudobulks

## cluster sizes

## pseudopresences

```{r}

result.list <- calculatePseudobulks(pbmck3k.seurat)

```

# computing minimal expression cutoff for each clusters pseudobulks

```{r}

expression.mat <- predictMinimalExpression(result.list)

```

# computing stability cutoff for each clusters pseudopresence

```{r}

pseudopresence.list <- predictPseudopresenceStability(result.list)

```

# computing relative difference for each clusters pseudobulks

```{r}

rel_diff.mat <- normaliseOnSEGs(result.list$pseudobulks.sm)

```

# computing ranges on relative difference 

```{r}

rel_diff_ranges.mat <- getNormalisedRanges(rel_diff.mat)

```

# computing clrs on relative difference

```{r}

clrs.mat <- transformToCLR(rel_diff.mat)

```

# computing intersect of single cell on bulk

```{r}

sc_on_bulk_intersect.mat <- calculateNormalisedIntersects(rel_diff.mat, dynamic_ranges.char = 'bulk_ranges')

```

# computing intersect of single cell on single cell

```{r}

sc_on_sc_intersect.mat <- calculateNormalisedIntersects(rel_diff.mat, dynamic_ranges.char = 'tabula_sapiens_ranges')

```

